LaTeX draft for \\"Ancient Greece Yuri Visual Novel"

### 2015-09-28 text/draft.tex
Introduce Antiope name

From so close, it's obvious I'm at least half a head taller than her, which never ends to surprise me. She looks big in everyday life, thanks to her headstrong confidence and athletic build, but is actually pretty average when using factual measurements.

\dcomment{
	Drop Antiope's name, using her athletic physique as a starting point.
}

@@

\speaker{Antiope} "Ambrosia, where have you been? I looked after you when the party started, but you were nowhere to be found."\\

@@

>>>>

From so close, it's obvious I'm at least half a head taller than her, which never ends to surprise me. She looks big in everyday life, thanks to her headstrong confidence and athletic build, but is actually pretty average when using factual measurements.\\

@@

\speaker{Her} "Ambrosia, where have you been? I looked after you when the party started, but you were nowhere to be found."\\

@@

On the opposite side, despite my talents as a singer, I'm unable to breath proper life into her own name. I pronounce it perfectly, but it sounds so bland when it should ring like the thunder in the summer sky. \emph{Antiope!} A warrior name, an amazon name, a mythological name, yet one escaping me as her bearer escapes me.\\
